The aims of science and an open science controversy at USEPA

### 2025-05-10 paper/paper.qmd
bibfile

@@

<!-- 
BJPS submission guidelines: 
<https://www.journals.uchicago.edu/journals/bjps/instruct>

>>>>

bibliography: "st_text_mining.yaml"

@@

<!-- 
PHOS submission guidelines: 
<https://www.cambridge.org/core/journals/philosophy-of-science/information/author-instructions>

Articles are limited to 9000 words, inclusive of abstract, footnotes, in-text citations, and appendices intended to appear with the manuscript.  Reference sections and online-only appendices are not included in the word count.

BJPS submission guidelines: 
<https://www.journals.uchicago.edu/journals/bjps/instruct>
